UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-17 paper/paper.tex
updates

%%%%%%%%%%%%%%%%%%%%%%
%%% IMPLEMENTATION 
%%%%%%%%%%%%%%%%%%%%%%

\chapter{Implementation}

\emph{/* Implementation quirks related to make it work. Mostly map/reduce jobs written for Apache Spark. */}

@@

\subsubsection{Threshold based report}

\subsubsection{Visual recognition}

@@

\section{Algorithm walkthrough}
\subsection{Calculate cost per hour for a given pricing scheme}
Results for ccs2.xlarge based on data published for AWS~\cite{AWS:2014} \par
\csvautotabular{out}
\subsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}
%\includegraphics[width=\linewidth]{cph}
\subsection{Collect VM usage data}
\subsection{Group usage metrics by machine}
\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}
\subsection{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}

>>>>

@@

@@

\section{Uptime Based Distance From Intersection Points}

Machines in Google Cluster Trace dataset do not have any pricing data attached. For further evaluation purposes, we have to assign example pricing schemes to each virtual machine.

Total number of machines: 12583
0.5 and 0.5,0.25 = 10595 = 84.2\% = heavy
rest = 1988 = 15.8\% = medium

Pricing: cc2.8xlarge
c_medium = upfront : 4146, perhour : 0.54 
c_heavy = upfront : 5000, perhour : 0.361
